\section{Workload Runtime}

FIXME: pull in description from Dong's WRAP document.

\newpage
\subsection{Workload Runtime WBS}

\begin{longtable}{|p{1cm}|p{10.2cm}|p{1cm}|p{1cm}|p{1.8cm}|}\hline
  \textbf{Item} & \textbf{Description}
                & \textbf{Deliv}\footnote{SD = software drop,
                        DR = design review, V = viewgraphs, D = document}
                & \textbf{Weeks} & \textbf{Depend} \\
  \hline
  \hline
  \multicolumn{5}{|l|}{4.1. \textbf{Runtime Basic Building Blocks}} \\
  \hline
  4.1.1.& Process manager command/control communication protocol design.
          (comms co-design)
        & DR, D
        & 
        & \\
  \hline
  \multicolumn{2}{|l|}{\em Note to Dong: agg/reduct framework moved to comms
              framework WBS}
        &
        &
        & \\
  \hline
  4.1.3.& Distributed key-value store name scoping specification and API.
          (comms co-design)
        & DR, D
        & 
        & \\
  \hline
  4.1.4.& Distributed key-value store investigation.  Evaluate servers
          via direct put/get methods using bootstrap and MPIR emulation.
        & V
        & 
        & \\
  \hline
  4.1.5.& Power control: Investigate  RAPL and ways to control power bound.
        & DR, D
        & 
        & RM \\
  \hline
  4.1.6.& Implement ProcMan communication protocol, DKVS name scoping API,
          direct key-value store, power controller.
        & SD
        & 
        & 4.1.1, 4.1.2, 4.1.3, 4.1.4, 4.1.5 \\
  \hline
  \multicolumn{5}{|l|}{4.2. \textbf{Runtime Service Building Blocks}} \\
  \hline
  4.2.1.& Process manager: design/prototype ProcMan and API.
        & DR, D
        & 
        & comms, 4.1.1\\
  \hline
  4.2.2.& Topo-aware binding: design/prototype binding and mapping
          mechanism and APIs.
        & DR, D
        & 
        & RM, 4.1.*\\
  \hline
  4.2.3.& Remote DKVS: investigate DKVS via remote put/get/sync using
	  bootstrap and MPIR emulation.
        & V
        & 
        & comms, 4.1.3(?), 4.1.4\\
  \hline
  4.2.4.& Implement ProcMan, topology-aware binding, remote DKVS.
        & SD 
        & 
        & 4.2.1, 4.2.2, 4.2.3 \\
  \hline
  \multicolumn{5}{|l|}{4.3. \textbf{Runtime User Service Interfaces}} \\
  \hline
  4.3.1.& Design/prototype job function utilities such as job function
          launcher.
        & DR, D
        & 
        & 4.2.1, 4.2.2, 4.2.3 \\
  \hline
  4.3.2.& Design/prototype job function synchronizers
        & DR, D
        & 
        & 4.2.1, 4.2.2, 4.2.3 \\
  \hline
  4.3.3.& Design/prototype bootstrappers: PMI2, PMGR/COBO, LIBI
        & V
        & 
        & 4.2.1, 4.2.2, 4.2.3 \\
  \hline
  4.3.4.& Implement job function utility.
        & SD
        & 
        & comms, 4.3.1 \\
  \hline
  4.3.5.& Implement job function sync.
        & SD
        & 
        & comms, 4.3.2 \\
  \hline
  4.3.6.& Implement PMI2, PMGR/COBO, LIBI
        & SD
        & 
        & comms, 4.3.3 \\
  \hline
\end{longtable}
