\begin{abstract}
Resource management (RM) software is crucial to HPC
for efficient application execution. %on a set of resources.
%
However, growing numbers and types of compute resources
and a greater interplay among various resources 
(e.g., between compute clusters and a shared I/O cluster) 
%across the entire HPC center can render even 
can render even
the best-in-breed RM software increasingly ineffective.
HPC centers are at a junction where they require
a new paradigm for resource management
to meet the challenges of extreme scalability,
resource diversity, and increasing complexity of job and resource
constraints such as power budgeting.
Our response to this critical need is \flux, an RM software
framework that can solve the key RM challenges
in a simple, extensible, distributed, and autonomous fashion.
Its design targets a computing facility as one common pool
of diverse sets of resources to provide
efficient and informed scheduling decisions and flexible accommodation
of site-wide constraints.

Further, \flux\ employs a framework approach to facilitate 
the seamless integration of system monitoring and administration,
lightweight virtualization, and  parallel programming and tools
run-time systems.
In this paper, we discuss our vision for \flux, identify key design challenges
and concepts, and report our progress prototyping
key components.
We report preliminary results that show our run-time prototype
provides requisite properties such as high scalability
and easy integration, as well as interoperability among essential
run-time software programs. %elements such as MPI, run-time tools and middleware.
\end{abstract}
